Minimizing post shock forecasting error using disparate information

### 2020-05-28 manuscript/manuscript.tex
edit of manuscript and addition of simulation codes

\newtheorem{cor}{Corollary}
\newtheorem{lem}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{prop}{Proposition}
\theoremstyle{definition}
\newtheorem{remark}{Remark}
\hypersetup{
  linkcolor  = blue,
  citecolor  = blue,
  urlcolor   = magenta,
  colorlinks = true,
} % color setup

@@

\begin{enumerate}
  \item Figure 1 is updated.
  \item Some introductions for forecast combination are added in Paragraph 2. Literature review for time-series pooling in cross-sectional (panel) data is rewritten and more to be added.
  \item The procedure for parametric bootstrap is rewritten.
  \item Technical details for SCM method are updated.
  \item SCM code is written using \texttt{Rsolnp} package.
\end{enumerate}

@@

Data integration for forecasting is a broad area of research including ideas from many areas. \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration %estimate posterior parameters for Richards model 
to improve predictive precision of COVID-19 infection trajectories for different countries. A similar setup may be beneficial for post-shock prediction but may be too dependent upon model specification for the shock distribution.
%, and conditions for predictive improvement are generally hard to know. 
\citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using clustering. However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool. \textbf{Mention synthetic intervention paper here, stress the importance of carefully constructing the donor pool.}  \emph{\textcolor{red}{More to be added ...}}

@@

\begin{figure}[H]
  \begin{center}
    \includegraphics[height = 8cm]{comp.pdf}
    \caption{A comparison between forecast without considering shock effects and the one uses simple averaging given $n=40$ disparate time series and that the shock time is at $T_1^* = 125$. The dots represent least square estimate $\hat{\alpha}_i$ from disparate time series. Two model differs by an adjustment $\hat{\alpha}=\frac{1}{n}\sum_{i=1}^n \hat{\alpha}_i$. \textbf{The picture needs to be made more clear. Remove $\hat{\alpha}_i$ and state what those points are in the caption. Label the true (unknown to us) shock effect $\alpha_1$.}}\label{figure1}
  \end{center}  
  \vspace{-.6cm}
\end{figure}

Figure \ref{figure1} provides simple intuition of the practical usefulness of our proposed methodology. This figure depicts a time-series that experienced a ``shock'' at time point $T_1^* = 125$. It is supposed that the researcher does not have any information beyond $T_1^*$, but does have observations of forty disparate time series that have previously undergone a similar shock for which post-shock responses are recorded. Similarity in this context means that the shock effects are random variables that from a common distribution.
%As we can see, the purple line provides a better prediction than the red line in this particular example. But we will justify later that consideration of estimated shock-effects will improve the prediction under certain conditions.
In this example, the mean of the estimated shock effects is taken as a shock-effect estimator for the time series under study. Forecasts are then made by adding this shock-effect estimator to the estimated response values obtained from the process that ignores the shock. It is apparent from Figure \ref{figure1} that adjusting forecasts in this manner 1) leads to a reduction in forecasting risk; 2) does not fully recover the true shock-effect. We evaluate the performance of this post-shock prediction methodology throughout this article; we outline situations for when it is expected to work and when it is not.

@@

for $t = 1,\ldots,T_i$ and $i = 1,\ldots, n+1$, where $D_{i,t} = 1(t > T_i^*)$, 

@@

  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*}+\gamma_i'\mbf{x}_{i, T^*_i-1}+\t{\varepsilon}_{i, T_i},

@@

$\tilde{\alpha}_i=\mu_{\alpha}+\delta_i'\mbf{x}_{i, T_i^*}+\gamma_i'\mbf{x}_{i, T_i^*-1}$. 

@@

We use similar notation as that in \cite{abadie2010synthetic} to motivate 
our weighted-adjustment estimator. Consider a $n\times 1$ weight vector 
$\mbf{W}=(w_2, \ldots, w_{n+1})$, where $w_i\in [0,1]$ for all 
$i = 2, \ldots, n+1$. Construct
\begin{align*}
 \mbf{X}_1 = \begin{pmatrix}
    \mbf{x}_{1, T_1^*-1} \\ \mbf{x}_{1, T_1^*}
  \end{pmatrix}
  \quad \text{ and }
  \quad  \hat{\mbf{X}}_1(\mbf{W})
  = w_2\begin{pmatrix}
     \mbf{x}_{2, T_2^*-1} \\
      \mbf{x}_{2, T_2^*}
   \end{pmatrix} + \cdots + w_{n+1} \begin{pmatrix}
     \mbf{x}_{n+1, T_{n+1}^*} \\
      \mbf{x}_{n+1, T_{n+1}^*}
   \end{pmatrix} .
\end{align*}
where $\mbf{X}_1$ and $\hat{\mbf{X}}_1(\mbf{W})$ are $2 \times p$. Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon w_2+ \cdots + w_{n+1}=1 \}$. 
Suppose there exists $\mbf{W}^*\in \mc{W}$ with 
$\mbf{W}^*=(w_2^*, \ldots, w_{n+1}^*)$ such that
\begin{align}
 \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*)  \quad i.e., \quad \mbf{x}_{1, T_1^*-1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*-1} \text{ and } \mbf{x}_{1, T_1^*} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*}.\label{SCM}
\end{align}
 Notice that $\mbf{W}^*$ exists as long as $\mbf{X}_1$ falls in the convex hull of 
 \begin{align*}
   \left\{ \begin{pmatrix}
     \mbf{x}_{2, T_2^*-1} \\
      \mbf{x}_{2, T_2^*}
   \end{pmatrix}, \ldots, \begin{pmatrix}
     \mbf{x}_{n+1, T_{n+1}^*} \\
      \mbf{x}_{n+1, T_{n+1}^*}
   \end{pmatrix} \right\}.
 \end{align*}
%It is a reasonable assumption that the pool of time series that we are considering 
%should be similar to the time series of interest. 
Our weighted-adjustment estimator will therefore perform well when the pool of 
disparate time series posses similar covariates to the time series for which 
no post-shock responses are observed. We compute $\mbf{W}^*$ as
\begin{align}
  \mbf{W}^* = \argmin_{\mbf{W}\in \mc{W}} \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W})\big)}_{2p}. 
  \label{W}
\end{align}
%which is a more general form of $\mbf{W}^*$ for the case when $\mbf{X}_1$ does not fall in the convex hull of (\ref{convexhull}). 
\cite{abadie2010synthetic} commented that we can select $\mbf{W}^*$ 
so that (\ref{SCM}) holds approximately %so that the property of $\mbf{W}^*$ should 
%still hold approximately 
and that weighted-adjustment estimation techniques of this form are not 
appropriate when the fit is poor. 
Note that $\mbf{W}^*$ is not random since the covariates are assumed to be fixed. Since $\mc{W}$ is a closed and bounded subset of $\reals^n$,  $\mc{W}$ is compact. Because the objective function 
is continuous in $\mbf{W}$, $\mbf{W}^*$ will always exist. %Relying on this weight, 
%we are mainly interested in constructing the following adjustment estimator:
Our weighted-adjustment estimator for the shock effect $\alpha_1$ is
  \begin{align*}
    \hat{\alpha}_{\rm wadj} = \sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i
    \quad \text{ for } \quad \mbf{W}^* = \begin{pmatrix}
      w^*_2 & \cdots & w^*_{n+1}
    \end{pmatrix}.
  \end{align*}
%Different from \citet{abadie2010synthetic}, our construction customizes synthetic control methods to the setting of AR(1) model. To be more specific, notice that (\ref{SCM}) implicitly uses the covariates at $T_*$ the shock-time and $T_*-1$ the time point just before the shock. This model somehow accounts for the impact of past information on the shock-effects. 
Estimation properties of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm IVW}$, 
and $\hat{\alpha}_{\rm wadj}$ are discussed in the remaining sections.

@@

 \begin{enumerate}[label = (\roman*)]
    \item Under $\mc{M}_{1}$, $\E{\hat{\alpha}_{\rm adj}}=\E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha}$.
    \item Under $\mc{M}_{21}$, 
    \begin{align*}
      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{2} \sum_{i=2}^{n+1} \delta' \mbf{x}_{i, T_i^*} + \frac{1}{n} \sum_{i=2}^{n+2} \gamma' \mbf{x}_{i, T_i^*-1} 
      \quad \text{ and } \quad 
       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \delta'\mbf{x}_{1, T_1^*} + \gamma' \mbf{x}_{1, T_1^*-1}.
    \end{align*}
    \item Under $\mc{M}_{22}$,
    \begin{align*}
      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{2} \sum_{i=2}^{n+1} \mu_{\delta}' \mbf{x}_{i, T_i^*} + \frac{1}{n} \sum_{i=2}^{n+2}  \mu_{\gamma}'\mbf{x}_{i, T_i^*-1} 
      \quad \text{ and } \quad 
       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \mu_{\delta}'\mbf{x}_{1, T_1^*} + \mu_{\gamma}' \mbf{x}_{1, T_1^*-1}.
    \end{align*}
  \end{enumerate}
Formal justification for these results can be found in Appendix. Note that $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are not unbiased estimators for $\alpha_1$. Notice that under $\mc{M}_{1}$, $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm adj}$ are unbiased estimators for $\E{\alpha_1}=\mu_{\alpha}$ (see distributional details of $\alpha_1$ in Section \ref{modelsetup}). Nevertheless, $\hat{\alpha}_{\rm adj}$ is a biased estimator for $\E{\alpha_1}$ but $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator for $\E{\alpha_1}$ under both $\mc{M}_{21}$ and $\mc{M}_{22}$. Thus, we collect these results  as the following proposition.

@@

\textbf{I am not sure if all of this is necessary. This is a nice summary of the literature but I think that we only need the results that motivate our bootstrap procedure.}

In this section, we present a parametric bootstrap procedure for our AR(1) model (see Section \ref{modelsetup}) in approximating the distribution of our shock-effect estimators. %NO NEED TO OUTLINE IN THIS WAY: In the first step, we will introduce the pros and cons of this algorithm and refer the users to other alternatives. In the second step, we detail the procedure of boostrapping AR(1).
%%\citet{efron} introduces the bootstrapping method to approximate the distribution of a statistic using a \emph{random sample}. However, this method will fail for time-series data since serial correlation or time-dependent features exist in typical time-series model. 
In the AR($p$) model, the unobserved errors are assumed to be identically and independently distributed. In this setting, standard bootstrap methodology can be applied to resampling the residuals \citep{efron1986bootstrap}. The asymptotic accuracy for OLS parameter estimation is guaranteed under the order of $O(T^{-1/2})$ almost surely, where $T$ is the length of the time series \citep{berkowitz2000recent}. \citet{bose1988edgeworth} showed that it can be further improved to $o(T^{-1/2})$ almost surely under some regularity conditions. Nevertheless, the pseudo time series generated by this procedure are not stationary.

\citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series. However, the asymptotic accuracy of this procedure to OLS estimation is not known. Additionally, the asymptotic accuracy of this algorithm can be sensitive to the selection of $p$, the parameter of the geometric distribution (\textbf{what does this mean, what is the geometric distribution in this context?}). This issue is similar to that of the selection of block size in moving-block bootstrapping \citep{kunsch1989jackknife, liu1992moving}.  More work related to bootstrapping time series  can be referred to \citet{berkowitz2000recent}. It is up to the user in selecting which procedure to choose but under different assumptions on the time-series.

\textbf{We do not need to rewrite bootstrap algorithms that exist in the literature. We only need to write our algorithm. Emphasis needs to be placed on $T_i^*$being known, the pre and post $T_i^*$ sampling needs to be made explicit.}

@@

\SetKwInOut{Input}{Input}
\Input{$B$ --  the number of parametric bootstraps  \\ $S_i= \{\hat{\varepsilon}_{i, t} \colon t = 1, \ldots, T_i\}$ -- the collection of  residuals for $t = 1,\ldots, T_i$ \\ $\mc{P}_i$ -- the fitted AR(1) model for $i = 2, \ldots, n+1$

}

@@

  \For{$b = 1:B$}{
  \For{$i = 2, \ldots, n+1$}{
  Sample with replacement from $S_{i}$ to obtain $S_{i}^{(b)}\coloneqq \{\hat{\varepsilon}_{i, t}^{(b)} \colon t = 1, \ldots, T_i\}$

  Plug $S_{i}^{(b)}$ into $\mc{P}_i$ to generate the bootstrapped response $\mbf{Y}_i^{(b)}$

  Compute $\hat{\alpha}_i^{(b)}$ based on OLS estimation of AR(1) with $\mbf{Y}_i^{(b)}$ and covariates from $\mc{P}_i$
  }
    Compute $\hat{\alpha}_{\rm adj}^{(b)}$, $\hat{\alpha}_{\rm wadj}^{(b)}$, and $\hat{\alpha}_{\rm IVW}^{(b)}$ 
  }
   Compute the sample mean, and sample variance of $\hat{\alpha}_{\rm adj}^{(b)}$, $\hat{\alpha}_{\rm wadj}^{(b)}$, and $\hat{\alpha}_{\rm IVW}^{(b)}$.
 \caption{Parametric bootstrap for approximation for  mean and  variance of shock-effect estimators of $\alpha_1$.}
\end{algorithm}
\vspace{.2cm}

@@

The estimates yielded by Algorithm \ref{boots} provides an approximation for parameters involved in the risk-reduction conditions in Sections \ref{conditions} and \ref{comparisons}. In particular $\overline{\hat{\alpha}_{\rm wadj}}$, the sample mean of $\hat{\alpha}_{\rm wadj}^{b}$, will provide an approximation for $\E{\alpha_1}$ under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ since it is unbiased for $\E{\alpha_1}$ under those three configurations from Proposition \ref{unbiased}. Therefore, we can judge whether to use a shock-effect estimator, and choose between  shock-effect estimators by this method.

\textbf{We should include a brief simulation which shows that our bootstrap procedure works.}

@@

>>>>

\newtheorem{cor}{Corollary}
\newtheorem{lem}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{prop}{Proposition}
\theoremstyle{definition}
\newtheorem{remark}{Remark}
\hypersetup{
  linkcolor  = blue,
  citecolor  = blue,
  urlcolor   = blue,
  colorlinks = true,
} % color setup

@@

\begin{enumerate}
  \item Figure 1 is revised accordingly.
  \item The synthetic intervention paper and comment are added in the introduction. Other parts haven't been revised.
  \item Parametric bootstrap is updated with additional comments. 
  \item The background for Example section is written.
  \item SCM.R for SCM method and sim.R for simulation are added in Github.
\end{enumerate}

@@

Data integration for forecasting is a broad area of research including ideas from many areas. \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration %estimate posterior parameters for Richards model 
to improve predictive precision of COVID-19 infection trajectories for different countries. A similar setup may be beneficial for post-shock prediction but may be too dependent upon model specification for the shock distribution.
%, and conditions for predictive improvement are generally hard to know. 
\citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using clustering. However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool. From a machine learning perspective, \citet{agarwal2020two} proposed a model-free synthetic intervention  method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions. Among those methodologies, they share the implicit assumption that candidates  from donor pool should be similar. In other words, caution should be dedicated to the construction of donor pool; otherwise, the result will be expected not to be  robust to the noise introduced by the insimilar ones. \emph{\textcolor{red}{More to be added ...}}

@@

\begin{figure}[H]
  \begin{center}
    \includegraphics[height = 8cm]{comp.pdf}
    \caption{The time series experience a shock at $T_1^*+1=126$ with true shock effect $\alpha = 4.88$. The figure is a comparison between forecast without considering shock effects and the one uses simple averaging given $n=40$ disparate time series, and that the shock time is at $T_1^* +1=126$. The magenta dots represent least square estimate $\hat{\alpha}_i$ from disparate time series. The prediction of $\hat{y}^{2}_{T_1^*+1}$ and $\hat{y}^{1}_{T_1^*+1}$ differs only by an adjustment $\hat{\alpha}=5.22$. It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
  \end{center}  
  \vspace{-.6cm}
\end{figure}

Figure \ref{figure1} provides simple intuition of the practical usefulness of our proposed methodology. This figure depicts a time-series that experienced a ``shock'' at time point $T_1^*+1 = 126$. It is supposed that the researcher does not have any information beyond $T_1^*+1$, but does have observations of forty disparate time series that have previously undergone a similar shock for which post-shock responses are recorded. Similarity in this context means that the shock effects are random variables that from a common distribution.
%As we can see, the purple line provides a better prediction than the red line in this particular example. But we will justify later that consideration of estimated shock-effects will improve the prediction under certain conditions.
In this example, the mean of the estimated shock effects is taken as a shock-effect estimator for the time series under study. Forecasts are then made by adding this shock-effect estimator to the estimated response values obtained from the process that ignores the shock. It is apparent from Figure \ref{figure1} that adjusting forecasts in this manner 1) leads to a reduction in forecasting risk; 2) does not fully recover the true shock-effect. We evaluate the performance of this post-shock prediction methodology throughout this article; we outline situations for when it is expected to work and when it is not.

@@

for $t = 1,\ldots,T_i$ and $i = 1,\ldots, n+1$, where $D_{i,t} = 1(t = T_i^* + 1)$, 

@@

  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1}+\gamma_i'\mbf{x}_{i, T^*_i}+\t{\varepsilon}_{i},

@@

$\tilde{\alpha}_i=\mu_{\alpha}+\delta_i'\mbf{x}_{i, T_i^*+1}+\gamma_i'\mbf{x}_{i, T_i^*}$. 

@@

We use similar notation as that in \cite{abadie2010synthetic} to motivate 
our weighted-adjustment estimator. Consider a $n\times 1$ weight vector 
$\mbf{W}=(w_2, \ldots, w_{n+1})$, where $w_i\in [0,1]$ for all 
$i = 2, \ldots, n+1$. Construct
\begin{align*}
 \mbf{X}_1 = \begin{pmatrix}
    \mbf{x}_{1, T_1^*} \\ \mbf{x}_{1, T_1^*+1}
  \end{pmatrix}
  \quad \text{ and }
  \quad  \hat{\mbf{X}}_1(\mbf{W})
  = w_2\begin{pmatrix}
     \mbf{x}_{2, T_2^*} \\
      \mbf{x}_{2, T_2^*+1}
   \end{pmatrix} + \cdots + w_{n+1} \begin{pmatrix}
     \mbf{x}_{n+1, T_{n+1}^*} \\
      \mbf{x}_{n+1, T_{n+1}^*+1}
   \end{pmatrix} .
\end{align*}
where $\mbf{X}_1$ and $\hat{\mbf{X}}_1(\mbf{W})$ are $2 \times p$. Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon w_2+ \cdots + w_{n+1}=1 \}$. 
Suppose there exists $\mbf{W}^*\in \mc{W}$ with 
$\mbf{W}^*=(w_2^*, \ldots, w_{n+1}^*)$ such that
\begin{align}
 \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*)  \quad i.e., \quad \mbf{x}_{1, T_1^*} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*} \text{ and } \mbf{x}_{1, T_1^*+1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}.\label{SCM}
\end{align}
 Notice that $\mbf{W}^*$ exists as long as $\mbf{X}_1$ falls in the convex hull of 
 \begin{align*}
   \left\{ \begin{pmatrix}
     \mbf{x}_{2, T_2^*} \\
      \mbf{x}_{2, T_2^*+1}
   \end{pmatrix}, \ldots, \begin{pmatrix}
     \mbf{x}_{n+1, T_{n+1}^*} \\
      \mbf{x}_{n+1, T_{n+1}^*+1}
   \end{pmatrix} \right\}.
 \end{align*}
%It is a reasonable assumption that the pool of time series that we are considering 
%should be similar to the time series of interest. 
Our weighted-adjustment estimator will therefore perform well when the pool of 
disparate time series posses similar covariates to the time series for which 
no post-shock responses are observed. We compute $\mbf{W}^*$ as
\begin{align}
  \mbf{W}^* = \argmin_{\mbf{W}\in \mc{W}} \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W})\big)}_{2p}. 
  \label{W}
\end{align}
%which is a more general form of $\mbf{W}^*$ for the case when $\mbf{X}_1$ does not fall in the convex hull of (\ref{convexhull}). 
\cite{abadie2010synthetic} commented that we can select $\mbf{W}^*$ 
so that (\ref{SCM}) holds approximately %so that the property of $\mbf{W}^*$ should 
%still hold approximately 
and that weighted-adjustment estimation techniques of this form are not 
appropriate when the fit is poor. 
Note that $\mbf{W}^*$ is not random since the covariates are assumed to be fixed. Since $\mc{W}$ is a closed and bounded subset of $\reals^n$,  $\mc{W}$ is compact. Because the objective function 
is continuous in $\mbf{W}$, $\mbf{W}^*$ will always exist. %Relying on this weight, 
%we are mainly interested in constructing the following adjustment estimator:
Our weighted-adjustment estimator for the shock effect $\alpha_1$ is
  \begin{align*}
    \hat{\alpha}_{\rm wadj} = \sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i
    \quad \text{ for } \quad \mbf{W}^* = \begin{pmatrix}
      w^*_2 & \cdots & w^*_{n+1}
    \end{pmatrix}.
  \end{align*}
%Different from \citet{abadie2010synthetic}, our construction customizes synthetic control methods to the setting of AR(1) model. To be more specific, notice that (\ref{SCM}) implicitly uses the covariates at $T_*$ the shock-time and $T_*-1$ the time point just before the shock. This model somehow accounts for the impact of past information on the shock-effects. 
Estimation properties of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm IVW}$, 
and $\hat{\alpha}_{\rm wadj}$ are discussed in the remaining sections.

@@

 \begin{enumerate}[label = (\roman*)]
    \item Under $\mc{M}_{1}$, $\E{\hat{\alpha}_{\rm adj}}=\E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha}$.
    \item Under $\mc{M}_{21}$, 
    \begin{align*}
      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{2} \sum_{i=2}^{n+1} \delta' \mbf{x}_{i, T_i^*+1} + \frac{1}{n} \sum_{i=2}^{n+2} \gamma' \mbf{x}_{i, T_i^*} 
      \quad \text{ and } \quad 
       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \delta'\mbf{x}_{1, T_1^*+1} + \gamma' \mbf{x}_{1, T_1^*}.
    \end{align*}
    \item Under $\mc{M}_{22}$,
    \begin{align*}
      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{2} \sum_{i=2}^{n+1} \mu_{\delta}' \mbf{x}_{i, T_i^*+1} + \frac{1}{n} \sum_{i=2}^{n+2}  \mu_{\gamma}'\mbf{x}_{i, T_i^*} 
      \quad \text{ and } \quad 
       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \mu_{\delta}'\mbf{x}_{1, T_1^*+1} + \mu_{\gamma}' \mbf{x}_{1, T_1^*}.
    \end{align*}
  \end{enumerate}
Formal justification for these results can be found in Appendix. Note that $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are not unbiased estimators for $\alpha_1$. Notice that under $\mc{M}_{1}$, $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm adj}$ are unbiased estimators for $\E{\alpha_1}=\mu_{\alpha}$ (see distributional details of $\alpha_1$ in Section \ref{modelsetup}). Nevertheless, $\hat{\alpha}_{\rm adj}$ is a biased estimator for $\E{\alpha_1}$ but $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator for $\E{\alpha_1}$ under both $\mc{M}_{21}$ and $\mc{M}_{22}$. Thus, we collect these results  as the following proposition.

@@

In this section, we present a parametric bootstrap procedure for our AR(1) model (see Section \ref{modelsetup}) in approximating the distribution of our shock-effect estimators. %NO NEED TO OUTLINE IN THIS WAY: In the first step, we will introduce the pros and cons of this algorithm and refer the users to other alternatives. In the second step, we detail the procedure of boostrapping AR(1).
%%\citet{efron} introduces the bootstrapping method to approximate the distribution of a statistic using a \emph{random sample}. However, this method will fail for time-series data since serial correlation or time-dependent features exist in typical time-series model. 
In the AR($p$) model, the unobserved errors are assumed to be identically and independently distributed. In this setting, standard bootstrap methodology can be applied to resampling the residuals \citep{efron1986bootstrap}. \citet{bose1988edgeworth} showed that the asymptotic accuracy for OLS parameter estimation can be further improved from $O(T^{-1/2})$ to $o(T^{-1/2})$ almost surely under some regularity conditions. Nevertheless, the pseudo time series generated by this procedure are not stationary.

\citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series $\{X_n \colon n \in \mathbb{N}\}$. This algorithm generates a sequence of blocks of observations $B_{I_1, L_1}, B_{I_2, L_2}, \ldots$, where $B_{i,b}= \{X_i, X_{i+1}, \ldots, X_{i+b-1}\}$\footnote{for $j > N$, $X_{j}$ is defined to be $X_k$, where $k = j \hspace{-.1cm} \mod N$ and $X_0 = X_N$}; and the sampling stops when $N$ observations are reached. Note that the collection of random positions $\{I_n \colon n \in \mathbb{N}\}$ is a sequence of i.i.d. discrete uniform random variables; and the collection of random lengths $\{L_n \colon n \in \mathbb{N}\}$ is a sequence of  i.i.d. geometric random variables with parameter $p$. However, the consistency needs to be proved by a case-by-case analysis \citep[Page 66]{politis1999subsampling}. Additionally, the asymptotic accuracy of this algorithm can be sensitive to the selection of $p$. This issue is similar to that of the selection of block size in moving-block bootstrapping \citep{kunsch1989jackknife, liu1992moving}.  More work related to bootstrapping time series  can be referred to Chapters 3 and 4 in \citet{politis1999subsampling}, and \citet{berkowitz2000recent}. It is up to the user in selecting which procedure to choose but under different assumptions on the time-series.

@@

\SetKwInOut{Input}{Input}
\Input{$B$ --  the number of parametric bootstraps  \\  $\{(y_{i,t}, \mbf{x}_{i,t})\colon i = 2,\ldots, n+1, t = 0, \ldots, T_i\}$ -- the data\\ $\{T_i^* \colon i = 1, \ldots, n+1\}$ -- the time point just before the shock\\$\{\hat{\varepsilon}_{i, t} \colon t = 1, \ldots, T_i\}$ -- the collection of  residuals for $t = 1,\ldots, T_i$ \\ $\{\hat{\eta}_i, \hat{\alpha}_i, \hat{\phi}_i, \hat{\theta}_i, \hat{\beta}_i\colon i = 2, \ldots, n+1\}$ -- the OLS estimates \\
}

@@

  \For{$b = 1:B$}{
  \For{$i = 2, \ldots, n+1$}{

    Sample with replacement from $\{\hat{\varepsilon}_{i, t} \colon t = 1, \ldots, T_i\}$ to obtain $\{\hat{\varepsilon}_{i, t}^{(b)} \colon t = 1, \ldots, T_i\}$

     Define $y_{i,0}^{(b)}=y_{i,0}$

    \For{$t = 1,\ldots, T_i$}{

     Compute $y_{i,t}^{(b)}=\hat{\eta}_i +\hat{\alpha}_i 1(t=T_i^*+1)+\hat{\phi}_iy_{i,t-1}^{(b)}+\theta_i'\mbf{x}_{i,t} + \beta_i'\mbf{x}_{i, t-1}+\hat{\varepsilon}_{i,t}^{(b)}$
    }
    Compute $\hat{\alpha}_i^{(b)}$ based on OLS estimation of (\ref{equation1}) with $\{(y_{i,t}^{(b)}, \mbf{x}_{i,t}) \colon t= 0, \ldots, T_i\}$
  }
   Compute the $b$th shock-effect estimate $\hat{\alpha}^{(b)}_{\rm est}$ for $\mrm{est} \in \{\mrm{adj}, \mrm{wadj}, \mrm{IVW}\}$
  }
   Compute the sample mean, and sample variance of $\{\hat{\alpha}_{\rm est}^{(b)} \colon b = 1, \ldots, B\}$ for $\mrm{est} \in \{\mrm{adj}, \mrm{wadj}, \mrm{IVW}\}$
 \caption{Parametric bootstrap for approximation for  mean and  variance of shock-effect estimators of $\alpha_1$.}
\end{algorithm}
\vspace{.2cm}

@@

The estimates yielded by Algorithm \ref{boots} provides an approximation for parameters involved in the risk-reduction conditions in Sections \ref{conditions} and \ref{comparisons}. The almost-sure convergence results for $\hat{\alpha}_{\mrm{adj}}$  and $\hat{\alpha}_{\mrm{wadj}}$ follow naturally if we assume the regularity conditions outlined in  \citet{bose1988edgeworth}.
The proof for the case of $\overline{\hat{\alpha}_{\mrm{wadj}}}$, the sample mean of the bootstrapped weighted adjustment estimator, can be presented as below. As $B \to \infty$,
\begin{align*}
  \overline{\hat{\alpha}_{\mrm{wadj}}} \mid \Theta 
  = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)} \mid \Theta 
  = \sum_{i=2}^{n+1}w_i^* \frac{1}{B} \sum_{b=1}^B\hat{\alpha}_i^{(b)} \mid \Theta 
  \overset{a.s.}{\rightarrow} \sum_{i=2}^{n+1}w_i^* \alpha_i \mid \Theta=\E{\hat{\alpha}_{\rm wadj}|\Theta},
\end{align*}
The case for the sample variance of the bootstrapped weighted adjustment estimator would be similar. The same line of analysis holds for   adjustment estimator as well since  it is a linear combination of OLS estimates, and the weights are not random conditioned on $\Theta$ (see Section \ref{modelsetup}). Nevertheless, the case for $\hat{\alpha}_{\rm IVW}$ is slightly different because it is not a linear combination of OLS estimates with random weights. It is not clear with respect to whether similar consistency results holds for $\hat{\alpha}_{\rm IVW}$. We would claim that Algorithm \ref{boots} only provides an \emph{approximation} for the case of $\hat{\alpha}_{\rm IVW}$.

In particular $\overline{\hat{\alpha}_{\rm wadj}}$, the sample mean of $\hat{\alpha}_{\rm wadj}^{(b)}$, will provide an approximation for $\E{\alpha_1}$ under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ since it is unbiased for $\E{\alpha_1}$ under those three configurations from Proposition \ref{unbiased}. Therefore, we can judge whether to use a shock-effect estimator, and choose between  shock-effect estimators by this method.

We \emph{stress} that the above approximation is conditioned on $\Theta$. Under a random-effect structure (see Section \ref{modelsetup}), every true shock effect of a time series in reality is only an observed value from a population.
  For example, $\overline{\hat{\alpha}_{\rm wadj}}\overset{a.s.}{\rightarrow}\E{\hat{\alpha}_{\rm wadj}|\Theta}$ and $\overline{\hat{\alpha}_{\rm wadj}} \not\overset{a.s.}{\rightarrow}\E{\alpha_1}$ but $\E{\E{\hat{\alpha}_{\rm wadj}|\Theta}}=\E{\alpha_1}$.

The simulation for justification of the parametric bootstrap is provided in Section \ref{parametricbootstrapsimulation}.

@@

\subsection{Parametric bootstrap simulation}
\label{parametricbootstrapsimulation}

In this section, we present the simulation for the parametric bootstrap procedure for AR(1) outlined in Section \ref{varbootstrap}. The simulation is only provided for the adjustment estimator and weighted adjustment estimator since the weights for inverse-variance estimator are random and the true values of its moments are unknown.

\begin{center}
  \begin{tabular}{l|cccccc}
    & \multicolumn{6}{c}{Time series}\\
    & 1 & 2 & 3 & 4 & 5 & 6\\
   Length $T_i$ & 77 & 93 & 72 & 71 & 73 & 50 \\
   Shock Time  $T_i^*+1$ & 20 & 39 & 45 & 52 & 59 & 11 \\
   Autoregressive parameter $\phi_i$ & 0.540 & 0.961 & 0.654 & 0.547 & 0.266 & 0.197 
  \end{tabular}
\end{center}

\section{Example}

In this example we forecast Conoco Phillips stock prices in the midst of the coronavirus (COVID-19) recession. Specific interest is in predictions made after March 6th, 2020, the Friday before the stock market crash on March 9th, 2020. We will detail how we  combine knowledge from disparate time series to improve the forecast of Conoco Phillips stock price without adjustment for the shock. The forecast consists of four steps: (1) pick a model, (2) selection of covariates,  (3) choices of donor pool, and (4) nowcast. Section \ref{background} provides the justification for the first three steps. Section \ref{results} discusses the result of our forecast.
